External validation

### 2020-09-03 diagnostics/README.Rmd
include figs for readme

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: show
    keep_md: yes
  md_document:
    variant: markdown_github
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

@@

```{r}
# Load the exported model object
load("../cache/fit_brl_reduced_lean.RData")
fit_brl_reduced_lean
```

@@

Those were the inclusions/exclusions from Sweden. Similar criteria should apply also for the external validation data set in to get comparable cohorts.

@@

```{r}
# Object I use on my end, which includes patient data and can therefore not be shared
head(ext_val_required_data) 
```

>>>>

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  github_document:
    toc: yes
    df_print: "kable"
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

@@

```{r}
# Load the exported model object
load("../cache/fit_brl_reduced_lean.RData")
```

@@

Those were the inclusions/exclusions from Sweden. Similar criteria should apply also for the external validation data set to get comparable cohorts.

@@

```{r}
head(ext_val_required_data) 
```
